Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-01-07 ms/ms06_floats.tex
ENH update

% full size table is table
\begin{table}[!tbp]
\centering
\scriptsize
%\hline
\csvreader[
separator=tab,
tabular=p{0.09\textwidth}p{0.09\textwidth}p{0.09\textwidth}p{0.09\textwidth}p{0.09\textwidth}p{0.09\textwidth}p{0.45\textwidth},
head,
table head=\bfseries Chrom & \bfseries Pleio RSID & \bfseries Pleio pos. & \bfseries Cytob. & \bfseries Start & \bfseries End & \bfseries GWAS Categories\\\hline,
]{\floatRelativePath/cmpt_pleiotropic_regions.py/100000/region_window_ms.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi\ & \csvcolvii}% specify your coloumns here
%\hline
%
\vspace{15pt}
\caption{Pleiotropic regions involving 7 or more GWAS classes. These regions were built with a sliding window of 1e5 nt. Genomic coordinates are given for the hg38 assembly.}\label{tab:pleiotropic_regions}
\end{table}

>>>>

% full size table is table
\begin{table}[!tbp]
\centering
\scriptsize
%\hline
\csvreader[
separator=tab,
tabular=p{0.02\textwidth}p{0.09\textwidth}p{0.09\textwidth}p{0.05\textwidth}p{0.09\textwidth}p{0.09\textwidth}p{0.45\textwidth},
head,
table head=\bfseries Chr. & \bfseries Start & \bfseries End & \bfseries Cytob. & \bfseries Pleio RSID & \bfseries Pleio pos. & \bfseries GWAS Categories\\\hline,
]{\floatRelativePath/cmpt_pleiotropic_regions.py/100000/region_window_ms.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolv\ & \csvcolvi\ & \csvcoliv\ & \csvcolii\ & \csvcoliii\ & \csvcolvii}% specify your coloumns here
%\hline
%
\vspace{15pt}
\caption{Pleiotropic regions involving 6 or more GWAS classes. These regions were built with a sliding window of 1e5 nt. Genomic coordinates are given for the hg38 assembly.}\label{tab:pleiotropic_regions}
\end{table}
